% Introduction :

\section{Introduction}

% Why did we do the work?
% What were the central motivations and hypotheses?
% The objectives of the work?
% What will this work show the reader?
% Why is it important?
% What should the reader watch for in the paper?
% What are the interesting high points?
% What strategy did we use?
% What should the reader expect as conclusion?


As nuclear power expands both domestically and internationally, nuclear fuel cycle
performance analysis on technical, economic, political, and environmental axes increases 
in importance. Appropriate nuclear fuel cycle analysis requires calculation of myriad physical, nuclear, 
chemical, industrial, and political phenomena. Nuclear fuel cycle simulators 
therefore couple complex systems such as nuclear process physics, 
facility deployment, and material routing. However, most nuclear fuel cycle 
simulators have not incorporated modern insights from simulation science and 
software architecture that can enable more efficient, accurate, robust, and 
validated analysis. 

The \Cyclus nuclear fuel cycle simulator framework and 
its modeling ecosystem address this need for a next-generation nuclear fuel cycle 
simulator. This dynamic simulator employs discrete agents, time, and isotopic resolution of materials 
and supports a range of analysis types, levels of 
detail, and analyst sophistication.
Additionally, \Cyclus employs a modular architecture and 
open development process that supports user access and 
encourages developer extensions.

Historically, nuclear fuel cycle simulators have estimated 
nuclear fuel cycle performance using software 
ranging from ad hoc spreadsheet-driven flow calculators to highly specialized 
system dynamics
proprietary models. To date, current tools are either static, fleet-based, 
privately distributed, or all of the above. Each of these qualities presents a 
severe challenge to modeling fidelity, generality, efficiency, robustness, and 
scientific transparency. 

An alternative to these approaches is a dynamic, agent-based simulator with an 
open platform and an ecosystem of research-driven capabilities.  
Dynamic nuclear fuel cycle analysis more realistically 
supports a range of simulation goals than static analysis 
\cite{piet_dynamic_2011}. Similarly, experience in the broader field of systems 
analysis indicates that agent-based modeling enables more flexible simulation 
control, without loss of generality \cite{macal_agent-based_2010}. Finally, openness 
allows cross-institutional collaboration, increases code robustness, and 
cultivates an ecosystem of calculation options 
\cite{softwarecarpentryresource}.  The fundamental concepts of the \Cyclus 
nuclear fuel cycle simulator capture these modern insights so that challenges 
in nuclear fuel cycle analysis can be better addressed. 

\subsection{Background}

% Who else has done what?
% How did they do that?
% What did we do before this?
% What is new?

% Common goals of fuel cycle simulation/simulators (driving &d focus,
% approximating tech. impacts, etc.)
% Previous work (cite all the tools!)
% Limitations of previous simulators by others (fleet-based, closed
% development, inflexible infrastructure)
% Previous attempts by this group (GENIUS v1/v2)
% note NGFCS

Nuclear fuel cycle simulators drive \gls{RDD} by calculating `metrics', 
quantitative measures of performance that 
can be compared among fuel cycle options. The feasibility of technology 
strategies, dynamics of transitions between fuel cycles, and many other 
measures of performance can be expressed in terms of these metrics. For example, 
economic feasibility is often measured in \gls{LCOE}, requiring calculation of
lifetime fuel costs and electricity generation, 
while environmental performance might be measured in spent fuel volume, 
  toxicity, or mined uranium.

Historically, the national laboratories have driven development and regulated 
the use of their own tools: \gls{VISION}\cite{jacobson_verifiable_2010}, 
\gls{DANESS}\cite{van_den_durpel_daness_2009}, 
\gls{DYMOND}\cite{yacout_modeling_2005}, and 
\gls{NFCSim}\cite{schneider_nfcsim:_2005}. 
Outside the national laboratories, researchers have created new nuclear fuel cycle 
simulation tools when existing tools were not available or not sufficiently 
general to calculate their metrics of interest with their method of choice.  
With limited access to the national laboratory tools and a need to customize 
them for research purposes, universities and private industry researchers have 
``reinvented the wheel'' by developing tools of their own from scratch and 
tailored to their own needs, for example \gls{CAFCA}\cite{guerin_impact_2009} and 
\gls{COSI}\cite{boucher_cosi_2005,boucher_cosi:_2006,meyer_new_2009,coquelet-pascal_comparison_2011}. 

This trend has resulted in a proliferation of specialized
fuel cycle simulators for the calculation of fuel cycle metrics.  Accordingly, methods 
for calculating those metrics vary among simulators. Some model the 
system of facilities, economics, and materials in static equilibrium, while 
other simulators capture the dynamics of the system.  
Similarly, while some simulators discretely model material and facilities, 
others treat materials as streams and facilities as fleets, in an aggregated 
fashion. Simulators often overspecialize, 
modeling a single aspect of the fuel cycle in great detail while neglecting 
others. For example, a simulator created for policy modeling might have excellent 
capability in economics while material isotopics and transmutation detail are 
neglected.

\Cyclus emerged from a line of tools seeking to break this practice.  
Its precurser, \gls{GENIUSv1}\cite{dunzik-gougar_global_2007,jain_transitioning_2006}, was begun at \gls{LDRD}, began at \gls{INL} and sought 
to provide generic regional capability.  Based on lessons learned from 
Version 1, the 
\acrshort{GENIUSv2} Version 2\cite{oliver_studying_2009,huff_geniusv2_2009} code sought to 
provide more generality and an extensible interface to facilitate 
collaboration.  The \Cyclus project then improved upon the \acrshort{GENIUSv2} 
effort by implementing increased modularity and encapsulation.  The result is  
a dynamic simulator that treats both materials and facilities discretely, with 
an architecture that permits simulations with multiple and variable levels of 
fidelity. The simulator's agent-based framework for tracking the 
transformation and trade of resources between facilities within institutions 
and regions greatly improves upon the existing fuel cycle simulators.

\subsection{Motivation}
% Gently reiterate the above need. 
% There should be a hero narrative here
% There was a gap in the capabilities of simulators.
% \Cyclus, a hero, came in to fill that gap. 

In addition to providing the fundamental features expected in fuel cycle 
simulators, the \Cyclus paradigm enables essential capabilities that previous 
simulators lack. Critically, its \emph{modular and open architecture}  facilitates 
targeted contribution and collaboration within the nuclear fuel cycle analysis 
community.  Additionally, \emph{agent interchangeability} facilitates direct 
comparison of modeling methodologies. Finally, the flexibility and generality 
of its \emph{\gls{ABM}} paradigm and \emph{discrete, object-oriented approach} 
enables \Cyclus to be applicable to a broader range of 
fidelities, scales, and applications than to other simulators. 

\Cyclus separates the problem of modeling a
physics-dependent supply chain into two distinct components: a simulation kernel and archetypes that
interact with the kernel. The kernel is responsible for the
deployment and interaction logic of entities in the simulation.  Physics calculations and 
customized behaviors are implemented within archetypes. Accordingly, specialists
in a given field can utilize their time and resources in modeling a specific
process associated with the nuclear fuel cycle (e.g., reprocessing and advanced
fuel fabrication), without having to model the entirety of the cycle.

Furthermore, modeling the evolution of a physics-dependent, international nuclear fuel supply
chain is a multiscale problem, and existing tools are not sufficiently 
multiscale. Tools have either focused on macro effects, e.g., the fleet-level
stocks and flows of commodities, or micro effects, e.g., the used-fuel
composition of fast reactor fuel. Each focus has driven the
development of specialized tools, rendering the task of answering questions between
the macro and micro levels challenging within a single tool. 
In constrast, the extensible architecture and discrete object tracking of \Cyclus allow
the creation and interchangeability of custom archetypes at any level of fidelity.


\subsubsection{Modular Architecture}
% Motivation for encapsulated plug-in architecture 
% enables ecosystem, ease of contribution across institutions
% enables myriad levels of simulation fidelity
% enables FC analyses that can compare ‘apples to apples'

The architecture of \Cyclus allows developers 
to define nuclear fuel cycle agents and processes independent of the simulation 
logic. This encapsulated `plug-in'
design choice provides two major benefits. First, analysts across research institutions can take advantage of the 
simulation logic \gls{API} and archetype ecosystem when they apply \Cyclus to 
their specific problem. This 
mend-and-extend paradigm, common in modern software development, reduces 
maintenance overhead and improves code robustness \cite{citation_needed}. 
The researcher can focus on creating or customizing nuclear 
facility, institution, resource, and toolkit models within their specific area 
of technical expertise. This extensibility, magnified by an open source 
development process, frees the community of users to contribute desired 
features, independent from the team of \Cyclus core developers. 
% we could use a specific example of Cosi's equivalence method below
Second, because \Cyclus uses a modular archetype approach, comparing two 
archetypes is straightforward. Consider a case in which an analyst would like 
to compare the effect of using different models to determine the input fuel 
composition for fast reactors. A variety of fuel fabrication archetypes can be 
developed and interchanged while keeping the rest of the fuel cycle fixed
 to compare fuel fabrication designs.

\subsubsection{Agent-based Paradigm}
% superior detail in capturing simulation dynamics
% more flexible control over behavior
% describe Region/Institution/Facility hierarchy
% note importance of generic resource exchange paradigm

\Cyclus implements an \gls{ABM} paradigm.  \gls{ABM} is modern, sophisticated, 
true to reality, and it incorporates modern computing resources.  
Furthermore, \gls{ABM} provides a natural 
perspective from which to model a given problem. In the nuclear fuel cycle 
context, for example, an analyst can design an agent with reactor-related logic 
that is entirely independent from an agent with fuel fabrication-related 
logic. Defining the behavior of both agents according to the 
\gls{API} contract is sufficient for them to interact with one another as 
bona fide actors in the simulation.  The two archetype libraries can be used in the same
simulation without any shared knowledge.

Furthermore, the \gls{ABM} paradigm is easily comparable to system dynamics models.
System dynamics is a popular approach for modeling nuclear fuel cycles 
\cite{jacobson_vision_2009,van_den_durpel_daness_2009,guerin_impact_2009,guerin_benchmark_2009}. 
Formally however, system dynamics models are simply a strict subset of agent-based models
\cite{macal_agent-based_2010}.
That is, any system dynamics model can be translated
into an agent-based model. Furthermore, because agent-based
techniques can provide a richer model than can system dynamics, they enable the 
broadest range of simulations in a generic fashion.

\subsubsection{Discrete Objects}
% enables more realistic models and metrics
% material routing metrics
% shadow fuel cycles
% etc.

\Cyclus models facilities, institutions, regions, and resources as discrete 
objects. A discrete resource model allows for a range of modeling granularity. In the
macroscopic extreme, it is equivalent to time-stepped continuous flow. In the
microscopic extreme, the model is capable of representing arbitrarily small 
material objects at isotopic resolution. In this way, \Cyclus is 
applicable across the full range of modeling extremes. 

Although some questions require resolution at the level of 
individual facilities and materials, 
Fleet-based, lumped-material models do not distinguish between discrete
facility entities or materials.  As a result, many detailed performance 
metrics cannot be captured with previously existing tools.
The generality of \Cyclus therefore enables many use cases 
that cannot be achieved with fleet-based models. 

One such use case seeks to capture system vulnerability to nefarious 
material diversion. Provenance and trade-history of distinct materials is the fundamental 
information unit in such studies, and so this type of analysis requires
 discrete simulation of a 
target facility and the individual materials modified within it. 
Provenance and trade-history of distinct materials is the fundamental 
information unit in such studies. 
Material risk analysis, therefore, demands discretely modeled objects like those 
in \Cyclus.

There are a number of types of users and developers who will 
interact with \Cyclus. National laboratory researchers,
academic researchers, private-industry economic forecasters, and even students 
in engineering courses may benefit from the ease of development and
customization provided by the discrete, modular, agent-based architecture of \Cyclus.
